---
title: "Loan Prediction WebApp"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 3
      bootswatch: cosmo
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(dplyr)
library(shiny)
library(plotly)
library(tidyverse)
library(caret)
library(viridis)
library(hrbrthemes)
library(ggplot2)
library(DT)
library(caTools)
library(caret)
library(markdown)
```

``` {r data}
loan_data<- read.csv("Loan (5).csv")
Numeric_variables<- c("Age","CCAvg","Mortgage" )
Categorical_Var <- c("Family", "Education","PersonalLoan", "SecuritiesAccount", "CDAccount", "Online", "CreditCard")

Ind_Var<- c("Income",  "Family",  "CCAvg", "Education" ,"CDAccount",  "Online", "CreditCard")

theme = theme_ipsum() + theme(plot.caption = element_text(hjust=0, size=8),
                                plot.title = element_text(hjust = 0, size=12, 
                                                          face="bold"),
                                axis.title.x = element_text(size=10),
                                axis.title.y = element_text(size=10))

#Models

loan_new<-loan_data %>%
  select(- c(ZIP.Code, Experience))

set.seed(123)
split <- sample.split(loan_new$PersonalLoan , SplitRatio = 0.7)
train_loan <- subset(x = loan_new , split == TRUE)
test_loan <- subset(x = loan_new, split==FALSE)

train_loan <- train_loan %>% 
  mutate(PersonalLoan = as.factor(PersonalLoan),
         SecuritiesAccount = as.factor(SecuritiesAccount))

library(pROC)
log_model2<- glm(PersonalLoan ~ Income + Family + CCAvg + Education + CDAccount + Online + CreditCard, data = train_loan , family = binomial(link="logit"))
pred_prob <- predict(object = log_model2, newdata = test_loan, type = "response")


```

Sidebar {.sidebar}
=====================================

```{r inputs}

selectInput("Categorical_Var", label = "Select Categorical Variable:", choices = Categorical_Var, selected = Categorical_Var[1])

selectInput("Numeric_variables", label = "Select Numeric Variable:", choices = Numeric_variables, selected = Numeric_variables[1])

selectInput("Ind_Var", label = "Choose one or more Indpendent Variable:", choices = Ind_Var, selected = Ind_Var[1], multiple = TRUE)


sliderInput(inputId="bw_adjust", label ="Density plot bandwidth adjustment:",
            min =0.2, max=2, value=1, step=0.2)

```

**Data description**
  
education level
(1) undergraduate 
(2) graduate
(3) advanced/professional

Securities : 1=Yes, 0=No
CDAccount : 1=Yes, 0=No
Online : 1=Yes, 0=No
CreditCard : 1=Yes, 0=No


Page1
==============================

Column {data-width=350}
-----------------------------------------------------------------------


### *BOXPLOT** Showing the relationship between Income and Education 

```{r }

renderPlotly(
  { plot_ly(loan_data, x = ~Education, y= ~ Income ,color = ~Education, type = "box") }
)

```

### DENSITY PLOT Showing the relationship between Numeric and Categorical Variable 

```{r density}

renderPlotly({
  p1 = ggplot(loan_new, aes_string(x=input$Numeric_variables, fill= 'input$Categorical_Var')) +
   geom_density(alpha = 0.4, bw = input$bw_adjust) +
    theme + scale_fill_viridis(discrete = T, alpha=0.8, option="A") 
  
  ggplotly(p1, res=100)
})

```

Column {data-width=400}
-----------------------------------------------------------------------

### BOX PLOT Showing the relationship between Numeric and Categorical Variable 

```{r}

renderPlotly({
  plot_ly(loan_new,
              x = ~loan_new[[input$Numeric_variables]],
              color = ~loan_new[[input$Categorical_Var]],
              colors = "Paired",
              type = "box") %>%
  layout(title = "",
         xaxis = list(title = "" ,
                      zeroline = FALSE))
})
```

### BARCHART Showing the relationship between Numeric and Categorical Variable 

```{r}

renderPlotly({
  loan_new %>%
    count(var = loan_new[[input$Categorical_Var]], name = "count") %>%
    plot_ly( x = ~var, y = ~ count, type = "bar", marker = list(color = '#008ae6',
                           line = list(color = '#008ae6', width = 2)), hoverinfo = "x+y") %>%
    add_text(text = ~paste0( " (",   scales::percent(count/sum(count)),")"), 
           textposition = "bottom", 
           textfont = list(size = 12, color = "white"), 
           showlegend = FALSE) %>%
    layout(xaxis = list(title = ""), yaxis = list(title = ""))
    
})


```



ML Model
============================

```{r reactive expression}

model1 <- reactive({
  vars <- as.matrix(loan_data[, input$Ind_Var])
  glm(PersonalLoan ~ Income + Family + CCAvg + Education + CDAccount + Online + CreditCard, data = train_loan , family = binomial(link="logit"))
})
```

Column {data-width=400}
-----------------------------------------------------------------------

### MODEL SUMMARY
```{r model output}

renderPrint({ 
   
summary(model1())

})

```

### ROC CURVE
```{r ROC}
test_roc = roc(test_loan$PersonalLoan ~ pred_prob, plot = TRUE, print.auc = TRUE)
```



Column {data-width=350}
-----------------------------------------------------------------------

### DATATABLE

```{r table2}
DT::renderDataTable({

 DT::datatable(train_loan %>% mutate(predicted = predict(model1()), residuals = residuals(model1())) %>% select(PersonalLoan, predicted, residuals), 
 rownames = FALSE, colnames = c('Actual Loan', 'predicted Loan', 'residuals'), extensions = c('Buttons', 'Responsive'), 
 options = list(columnDefs = list(list(className = 'dt-center', targets = "_all")), dom = 'Blfrt', 
 buttons = c('copy', 'csv', 'excel', 'print'), searching = FALSE, lengthMenu = c(20, 100, 1000, nrow(loan_new)), scrollY = 300, scrollCollapse = TRUE)) %>% 
 formatCurrency(c('PersonalLoan', 'predicted', 'residuals'))
 
})

```

### HISTOGRAM

```{r histogram1}
renderPlotly({
  

plot_ly(train_loan, x = ~round(residuals(model1()),2), type = "histogram", marker = list(color = "#EA6345",
                            line = list(color = "#FFFFFF", width = 1))) %>%   layout(title = '',
         yaxis = list(zeroline = FALSE, title = "frequency",  titlefont = list(
  family = "Lucida Console, Courier New, monospace", size = 12, color = "#FFFFFF"), 
  tickfont = list(
  family = "Lucida Console, Courier New, monospace", size = 10, color = "#FFFFFF"), color =  "white"),
         xaxis = list(zeroline = FALSE, title = "residual",  titlefont = list(
  family = "Lucida Console, Courier New, monospace", size = 12, color = "#FFFFFF"), 
  tickfont = list(
  family = "Lucida Console, Courier New, monospace", size = 10, color = "#FFFFFF"), color =  "white")) %>%
  layout(plot_bgcolor='#678EB9', paper_bgcolor='#678EB9')


})


```


# Table
```{r table}
renderDT(
  loan_data,
    filter = "top",server = FALSE,
    extensions = c('Buttons', 'Scroller'),
      options = list(
        dom = 'Blfrtip',
        buttons = c('csv', 'excel', 'pdf'),
        scrollY = '600px',
        scroller = TRUE
        )
    )
```
